Information Disclosure in Dynamic Innovation Contests

### 2025-06-14 paper/Paper.tex
update

%% Static Contest Design
% definition
A rich literature on \textit{static} contest design \citep{Ales2017Contest} investigates how to structure competitive environments to elicit optimal performance. 
These models typically rely on an explicit contest success function (CSF) that maps individual effort to winning probabilities \citep{skaperdas1996contest}.\footnote{There are exceptions like beauty or barrier contests.} 
Early contributions include \citet{Tullock1980}, \citet{Lazear1981tournaments}, and \citet{nalebuff1983Competition}. 
% application
This line of research is motivated by a wide range of real-world applications, including CEO selection \citep{tsoulouhas2006ceo}, beauty contests \citep{morris2002social}, election campaigns \citep{denter2020campaign}, advertising \citep{dockner2018Advertising}, litigation \citep{baik2007litigation, park2022litigation}, and innovation tournaments \citep{chen2021DataSharing}.
% design
Key design dimensions studied in the literature include optimal prize allocation \citep{moldovanu2001optimal, ales2017optimal_award}, participation rules \citep{Ales2021Innovation, stouras2022role}, contest duration\footnote{Static model in the sense that homogeneous participants make a single submission at the contest deadline, with no intermediate feedback provided throughout the process.} \citep{korpeoglu2021duration}, ex-ante handicapping of heterogeneous agents \citep{tsoulouhas2006ceo, kirkegaard2012favoritism, syam2013sales}, mechanisms addressing ex-post outcome imbalances \citep{Imhof2016Ex_post}, and information disclosure in auction-like environments \citep{bergemann2022optimal, antsygina2023optimal}.

@@

% One Way: Poisson Arrival of Innovation Success
One strand of the literature models dynamic contests as multistage processes, where participants exert effort over time while facing uncertainty about intermediate progress.
This structure facilitates the analysis of the mid-contest policy instruments available to the contest designer, such as feedback disclosure, screening mechanisms, etc.
Specifically, in a typical two-stage setting \citep{aoyagi2010information, mihm2019feedback}, the initial stage captures either feasibility uncertainty or foundational experimentation, with progress revealed through milestone feedback provided by the contest organizer. 
Participants exert effort in both stages, and the final output reflects the cumulative impact of early performance and subsequent improvement.
Similarly, \citet{Bimpikis2019Contest} study a two-stage model in which agents exert continuous effort to complete Stage A (potentially infeasible) and Stage B (feasible), with breakthroughs governed by Poisson processes.
In all these models, the contest designer may strategically disclose interim feedback.
Another example is \citet{Khorasani2023screening}, who analyze a two-stage contest in which solvers invest exploratory effort to generate viable ideas, with only those passing an imperfect screening mechanism proceeding to execution.

% Another Way of Modelling
The second approach, more closely related to our work, treats output as a stochastic process whose drift depends on the participant’s effort.
This line of research originates from the tug-of-war framework, first formalized by \citet{Harris1987Race} as a one-dimensional simplification of a multi-stage R\&D race.
Subsequent studies build on this foundation by modeling each player’s progress as a Brownian motion.
\citet{budd1993model}, for example, analyze a duopoly innovation race where the state evolves as a Brownian motion driven by the difference in effort, and characterize an approximate equilibrium.
\citet{Moscarini2011Contest} advance this approach by modeling the game state as the output gap between players and derive closed-form equilibrium strategies under pure-strategy play.
\citet{ryvkin2022fight} adapt their framework to a dynamic contest with a fixed deadline, providing a closed-form solution for the Markov perfect equilibrium.

%% Online Crowdsourcing
% this paper
This paper studies online crowdsourcing contests, which are typically characterized by 
$i$) fixed deadlines, 
$ii$) repeated submissions, and 
$iii$) public real-time feedback,
all governed by platform-specific rules and evaluation metrics.
% our foundation
Hence, our analysis builds on the model by \citet{ryvkin2022fight}, which, despite its simplifications, offers a closed-form solution that balances realism with analytical tractability. 
To better reflect the dynamics of online leaderboards, we depart from their full-information setting by introducing a noisy real-time public signal, thereby enhancing the model’s empirical relevance.

@@

% Dynamic contests
Most dynamic structural estimations rely on the Markov Perfect Equilibrium (MPE) of a dynamic game. 
However, when the model is calibrated to closely fit real-world data, the MPE typically lacks a closed-form solution.
For example, \citet{jiang2022role} develop a finite-horizon dynamic game with discrete time, state, and action spaces to model creators’ strategic behaviour in response to feedback during online logo design contests.
Using data from 810 contests, they implement a two-step maximum likelihood estimation (MLE) procedure under the assumption of ex-ante homogeneous contests and players: the first step estimates action-specific state transition probabilities, while the second recovers utility parameters.

@@

% Contest Deadline
Following \cite{ryvkin2022fight}, let's consider a dynamic contest with a fixed deadline. 
Suppose the contest is terminated when time $t=T>0$. 
Since the steady state estimation variance $\bar{S}$ is fixed as displayed above, the state of the game is fully characterized by a tuple $(\tilde{y}_t, t)$. 
At any time $0\le t<T$, player $i$ optimizes her effort level $q_{i,\tau}$ in the remaining contest period $\tau\in[t, T)$ according to the following optimization problem, 
\begin{equation}\label{v-def}
	V^i(\tilde{y}_{t}, t ; q_{j,t},\Theta_i) = \max_{\{q_{i,\tau}\}^T_{\tau=t}} 
	\mathbb{E}\left( \theta\cdot1_{\tilde{y}_T>0} - \int^T_tC_i(q_{i,\tau})d\tau \bigg|I_t\right) 
\end{equation}
where $\Theta_i \equiv\{\theta, \lambda, \sigma, c_i\}$, subject to constraints (\ref{filtered-x}), (\ref{filtered-S}) and $q_{i,\tau}\ge0$ for all $\tau\in[t,T)$.
The optimization problem for player $j$ is just symmetric to that of player $i$ as $V^j(\tilde{y}_t, t) = V^i(-\tilde{y}_t, t)$. 
The corresponding Hamilton-Jacobi-Bellman (HJB) equation for player $i$ is 
\begin{equation*}
0 = \max_{q_{i,t}\ge0}\left[-\frac{c_iq_i^2}{2} + V^i_{y}\cdot\left(q_{i,t}-q_{j,t}\right)+V^i_t + \frac{V^i_{yy}}{2}\lambda \bar{S}^2\right].
\end{equation*}
By definition, we have $\lambda \bar{S}^2 = \sigma^2$. 
Under the assumption of inner solution, we plug into the first order conditions $q_{i,t} = V^i_y/c_i$ and $q_{j,t} = -V^j_y/c_j$, we have the system of equations
\begin{equation*}
\begin{aligned}
\frac{1}{2c_i}(V^i_y)^2 + \frac{1}{c_j}V^i_yV^j_y + V^i_t + V^i_{yy}\frac{\sigma^2}{2} = 0\\
\frac{1}{2c_j}(V^j_y)^2 + \frac{1}{c_i}V^j_yV^i_y + V^j_t + V^j_{yy}\frac{\sigma^2}{2} = 0
\end{aligned}
\end{equation*}
subject to boundary conditions $V^i(-\infty, t) = 0$, $V^i(+\infty, t) = \theta$, $V^j(-\infty, t) = \theta$, $V^j(+\infty, t)=0$, $V^i(\tilde{y}_T, T) = \theta \cdot 1_{\tilde{y}_T > 0}$ and $V^j(\tilde{y}_T, T) = \theta \cdot 1_{\tilde{y}_T < 0}$.

@@

\begin{theorem}[\citealt{ryvkin2022fight}]
In the Markov perfect equilibrium, the players’ efforts in state $m_{i(j)}(\tilde{y}_t, t) :\mathbb{R}\times[0, T)\to\mathbb{R}_+$ are given by
\begin{equation}\label{eq-equilibrium-effort}
m_{i(j)}(\tilde{y}_t, t) = \frac{e^{-z^2/2}}{\sqrt{2\pi\sigma^2(T-t)}}\cdot \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]
\end{equation}
where $z = \tilde{y}_t / (\sigma\sqrt{T-t})$, $\rho(z) = \gamma^{-1}\left(\Phi(z)\left[\gamma(\rho_{i})+\gamma(\rho_{j})\right]-\gamma(\rho_{j})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},\quad u\in(-1,1)
\end{equation*}
\begin{equation*}
\rho_{i} = \frac{e^{w_{i}}+e^{-w_{j}}-2}{e^{w_{i}}-e^{-w_{j}}},
\quad
\rho_{j} = \frac{e^{w_{j}}+e^{-w_{i}}-2}{e^{w_{j}}-e^{-w_{i}}},
\quad
w_{i(j)} = \frac{\theta}{\sigma^2 c_{i(j)}}.
\end{equation*}
Moreover, the total expected effort at time $t$, defined by $M(\tilde{y}_t, t) := \mathbb{E}\left[\int^T_t m_i(\tilde{y}_s, s) + m_j(\tilde{y}_s, s)ds\right]$, is given by $M(\tilde{y}_t, t) = \sigma \sqrt{T-t} q(z)$, where $q(z)$ is determined by the ordanary differential equation 
\begin{equation}
\begin{aligned}
&q''(z) + \left[4A_+(z)e^{-z^2/2}+z\right]q'(z) - q(z) + 4A_-(z)e^{-z^2/2} = 0\\
&A_-(z) = \frac{\gamma(\rho_1) + \gamma(\rho_2)}{2\sqrt{2\pi}}[1 - \rho(z)^2],
\quad A_+(z) = A_-(z)\rho(z)
\end{aligned}
\end{equation}
subject to the boundary conditions $q(z)\to0$ as $z\to\pm\infty$. 
Specifically, when $c_i = c_j$, we have $w_i = w_j = w$ and the total expected effort is reduced to 
\begin{equation}\label{eq-totaleffort-reduced}
M(\tilde{y}_t, t) = \frac{2w\sigma\sqrt{T-t}}{\sqrt{2\pi}}e^{-z^2/2} + o(w)
\end{equation}
\end{theorem}

@@

For more properties of the equilibrium, please refer to \citet{ryvkin2022fight}. 
Here, we only provide a supplementary analysis related to contest design:

@@

When generating long-horizon contest data, it is important to appropriately lower the effort costs $c_i$ and $c_j$ to ensure sustained effort from the contestants.
This is because effort levels are influenced by the remaining time until the deadline:
according to equation~(\ref{eq-equilibrium-effort}), the further away the deadline, the lower the equilibrium effort. 
Moreover, with volatility held constant, a long contest duration increases the likelihood that the true output gap undergoes a random walk to an unusually high level, potentially resulting in unexpected early success \citep{ryvkin2022fight}.
These factors may affect the quality of the generated data.

@@

%%%%%%%%%% Figure & Table %%%%%%%%%%%
\noindent
\begin{minipage}[t]{0.43\textwidth}
	\vspace*{\fill}
	\centering
	\includegraphics[width=\linewidth]{validate_lamb.pdf}
	\vspace*{\fill}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\vspace*{\fill}
	\centering
	\newcolumntype{Y}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{llYY}
		\toprule
		& coef. & stderr & 95\% CI \\
		\midrule
		const.
		& -0.733 & 3.181 & [-7.073, 5.607] \\
		$\log(1 + \hat{\lambda})$ 
		& 3.264\textbf{**} & 1.088 & [1.096, 5.432] \\
		\midrule
		Obs. & \multicolumn{3}{c}{75} \\
		R$^2$ & \multicolumn{3}{c}{0.110} \\
		Adj. R$^2$ & \multicolumn{3}{c}{0.098} \\
		\bottomrule
		\addlinespace[0.5ex]
	\end{tabularx}
	\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) Significance levels: \textbf{***} $p < 0.001$, \textbf{**} $p < 0.01$, \textbf{*} $p < 0.05$. 
(2) Normality diagnostics: Omnibus = 0.378, Jarque-Bera = 0.071, Skewness = -0.042, Kurtosis = 3.126. 
(3) Other diagnostic statistics: Condition Number = 28.2, Durbin-Watson = 2.244.
}
	\end{minipage}
	\vspace*{\fill}
\end{minipage}
%%%%%%%%%%%% Captions %%%%%%%%%%%%
\noindent
\begin{minipage}[t]{\textwidth}
	\centering
	\captionof{figure}{$\lambda^{\text{MLE}}$ vs. Bayesian Estimate $\hat\lambda$}
	\label{fig-validate-lambda}
\end{minipage}
%\hfill
%\begin{minipage}[t]{0.53\textwidth}
%	\centering
%	\captionof{table}{Regression of $\lambda^{\text{MLE}}$ on Bayesian Estimate $\hat\lambda$}
%\end{minipage}
\medskip

The left panel of Figure~\ref{fig-validate-lambda} reveals a clear positive relationship between the log-transformed estimates of $\hat\lambda$ and $\lambda^{\text{MLE}}$.
In the accompanying regression table, we observe that the intercept is statistically insignificant, while the slope coefficient is estimated at 3.264 and is statistically significant at the 1\% level.
The regression residuals exhibit no significant deviation from normality, as indicated by the low Jarque-Bera statistic (0.071), near-zero skewness (-0.042), and kurtosis close to 3 (3.126). 
The condition number (28.2) suggests no severe multicollinearity, while the Durbin-Watson statistic (2.244) indicates no significant autocorrelation in the residuals. 
These diagnostics support the validity of the OLS assumptions.

It is worth noting, however, that the $R^2$ of the regression is relatively low, around 0.10, suggesting that the scatter points are not tightly clustered around the fitted line but instead show substantial dispersion.
This pattern likely reflects the limited sample size as well as the simplifying assumptions introduced during data processing and structural estimation.

>>>>

%% Static Contest Design
% definition
A rich literature on \textit{static} contest design \citep{ales2017optimal_award} investigates how to structure competitive environments to elicit optimal performance. 
These models typically rely on an explicit contest success function (CSF) that maps individual effort to winning probabilities \citep{skaperdas1996contest}.\footnote{There are exceptions like beauty or barrier contests.} 
Early contributions include \citet{Tullock1980}, \citet{Lazear1981tournaments}, and \citet{nalebuff1983Competition}. 
% application
This line of research is motivated by a wide range of real-world applications, including CEO selection \citep{tsoulouhas2006ceo}, beauty contests \citep{morris2002social}, election campaigns \citep{denter2020campaign}, advertising \citep{dockner2018Advertising}, litigation \citep{baik2007litigation, park2022litigation}, and innovation tournaments \citep{chen2021DataSharing}.
% design
Key design dimensions studied in the literature include optimal prize allocation \citep{moldovanu2001optimal, ales2017optimal_award}, participation rules \citep{ales2021number_of_players, stouras2022role}, contest duration\footnote{Static model in the sense that homogeneous participants make a single submission at the contest deadline, with no intermediate feedback provided throughout the process.} \citep{korpeoglu2021duration}, ex-ante handicapping of heterogeneous agents \citep{tsoulouhas2006ceo, kirkegaard2012favoritism, syam2013sales}, mechanisms addressing ex-post outcome imbalances \citep{Imhof2016Ex_post}, and information disclosure in auction-like environments \citep{bergemann2022optimal, antsygina2023optimal}.

@@

% One Way: Poisson Arrival of Innovation Success
One strand of the literature models dynamic contests as multistage processes, where participants exert effort over time while facing uncertainty about intermediate progress.
This structure facilitates the analysis of the mid-contest policy instruments available to the contest designer, such as feedback disclosure, screening mechanisms, etc.
Specifically, in a typical two-stage setting \citep{aoyagi2010information, mihm2019feedback}, the initial stage captures either feasibility uncertainty or foundational experimentation, with progress revealed through milestone feedback provided by the contest organizer. 
Participants exert effort in both stages, and the final output reflects the cumulative impact of early performance and subsequent improvement.
Similarly, \citet{bimpikis2019designing} study a two-stage model in which agents exert continuous effort to complete Stage A (potentially infeasible) and Stage B (feasible), with breakthroughs governed by Poisson processes.
In all these models, the contest designer may strategically disclose interim feedback.
Another example is \citet{Khorasani2023screening}, who analyze a two-stage contest in which solvers invest exploratory effort to generate viable ideas, with only those passing an imperfect screening mechanism proceeding to execution.

% Another Way of Modelling
The second approach, more closely related to our work, treats output as a stochastic process whose drift depends on the participant’s effort.
This line of research originates from the tug-of-war framework, first formalized by \citet{Harris1987Race} as a one-dimensional simplification of a multi-stage R\&D race.
Subsequent studies build on this foundation by modeling each player’s progress as a Brownian motion.
\citet{budd1993Duopoly}, for example, analyze a duopoly innovation race where the state evolves as a Brownian motion driven by the difference in effort, and characterize an approximate equilibrium.
\citet{Moscarini2007Contest} advance this approach by modeling the game state as the output gap between players and derive closed-form equilibrium strategies under pure-strategy play.
\citet{Ryvkin2022Fight} adapt their framework to a dynamic contest with a fixed deadline, providing a closed-form solution for the Markov perfect equilibrium.

%% Online Crowdsourcing
% this paper
This paper studies online crowdsourcing contests, which are typically characterized by 
$i$) fixed deadlines, 
$ii$) repeated submissions, and 
$iii$) public real-time feedback,
all governed by platform-specific rules and evaluation metrics.
% our foundation
Hence, our analysis builds on the model by \citet{Ryvkin2022Fight}, which, despite its simplifications, offers a closed-form solution that balances realism with analytical tractability. 
To better reflect the dynamics of online leaderboards, we depart from their full-information setting by introducing a noisy real-time public signal, thereby enhancing the model’s empirical relevance.

@@

% Dynamic contests
Most dynamic structural estimations rely on the Markov Perfect Equilibrium (MPE) of a dynamic game. 
However, when the model is calibrated to closely fit real-world data, the MPE typically lacks a closed-form solution.
For example, \citet{jiang2022feedback} develop a finite-horizon dynamic game with discrete time, state, and action spaces to model creators’ strategic behaviour in response to feedback during online logo design contests.
Using data from 810 contests, they implement a two-step maximum likelihood estimation (MLE) procedure under the assumption of ex-ante homogeneous contests and players: the first step estimates action-specific state transition probabilities, while the second recovers utility parameters.

@@

% Contest Deadline
Following \cite{Ryvkin2022Fight}, let's consider a dynamic contest with a fixed deadline. 
Suppose the contest is terminated when time $t=T>0$. 
Since the steady state estimation variance $\bar{S}$ is fixed as displayed above, the state of the game is fully characterized by a tuple $(\tilde{y}_t, t)$. 
At any time $0\le t<T$, player $i$ optimizes her effort level $q_{i,\tau}$ in the remaining contest period $\tau\in[t, T)$ according to the following optimization problem, 
\begin{equation}\label{v-def}
	V^i(\tilde{y}_{t}, t ; q_{j,t},\Theta_i) = \max_{\{q_{i,\tau}\}^T_{\tau=t}} 
	\mathbb{E}\left( \theta\cdot1_{\tilde{y}_T>0} - \int^T_tC_i(q_{i,\tau})d\tau \bigg|I_t\right) 
\end{equation}
where $\Theta_i \equiv\{\theta, \lambda, \sigma, c_i\}$, subject to constraints (\ref{filtered-x}), (\ref{filtered-S}) and $q_{i,\tau}\ge0$ for all $\tau\in[t,T)$.
The optimization problem for player $j$ is just symmetric to that of player $i$ as $V^j(\tilde{y}_t, t) = V^i(-\tilde{y}_t, t)$. 
The corresponding Hamilton-Jacobi-Bellman (HJB) equation for player $i$ is 
\begin{equation*}
0 = \max_{q_{i,t}\ge0}\left[-\frac{c_iq_i^2}{2} + V^i_{y}\cdot\left(q_{i,t}-q_{j,t}\right)+V^i_t + \frac{V^i_{yy}}{2}\lambda \bar{S}^2\right].
\end{equation*}
By definition, we have $\lambda \bar{S}^2 = \sigma^2$. 
Under the assumption of inner solution, we plug into the first order conditions $q_{i,t} = V^i_y/c_i$ and $q_{j,t} = -V^j_y/c_j$, we have the system of equations
\begin{equation*}
\begin{aligned}
\frac{1}{2c_i}(V^i_y)^2 + \frac{1}{c_j}V^i_yV^j_y + V^i_t + V^i_{yy}\frac{\sigma^2}{2} = 0\\
\frac{1}{2c_j}(V^j_y)^2 + \frac{1}{c_i}V^j_yV^i_y + V^j_t + V^j_{yy}\frac{\sigma^2}{2} = 0
\end{aligned}
\end{equation*}
subject to boundary conditions $V^i(-\infty, t) = 0$, $V^i(+\infty, t) = \theta$, $V^j(-\infty, t) = \theta$, $V^j(+\infty, t)=0$, $V^i(\tilde{y}_T, T) = \theta \cdot 1_{\tilde{y}_T > 0}$ and $V^j(\tilde{y}_T, T) = \theta \cdot 1_{\tilde{y}_T < 0}$.

@@

\begin{theorem}[\citealt{Ryvkin2022Fight}]
In the Markov perfect equilibrium, the players’ efforts in state $m_{i(j)}(\tilde{y}_t, t) :\mathbb{R}\times[0, T)\to\mathbb{R}_+$ are given by
\begin{equation}\label{eq-equilibrium-effort}
m_{i(j)}(\tilde{y}_t, t) = \frac{e^{-z^2/2}}{\sqrt{2\pi\sigma^2(T-t)}}\cdot \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]
\end{equation}
where $z = \tilde{y}_t / (\sigma\sqrt{T-t})$, $\rho(z) = \gamma^{-1}\left(\Phi(z)\left[\gamma(\rho_{i})+\gamma(\rho_{j})\right]-\gamma(\rho_{j})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},\quad u\in(-1,1)
\end{equation*}
\begin{equation*}
\rho_{i} = \frac{e^{w_{i}}+e^{-w_{j}}-2}{e^{w_{i}}-e^{-w_{j}}},
\quad
\rho_{j} = \frac{e^{w_{j}}+e^{-w_{i}}-2}{e^{w_{j}}-e^{-w_{i}}},
\quad
w_{i(j)} = \frac{\theta}{\sigma^2 c_{i(j)}}.
\end{equation*}
Moreover, the total expected effort at time $t$, defined by $M(\tilde{y}_t, t) := \mathbb{E}\left[\int^T_t m_i(\tilde{y}_s, s) + m_j(\tilde{y}_s, s)ds\right]$, is given by $M(\tilde{y}_t, t) = \sigma \sqrt{T-t} q(z)$, where $q(z)$ is determined by the ordanary differential equation 
\begin{equation}
\begin{aligned}
&q''(z) + \left[4A_+(z)e^{-z^2/2}+z\right]q'(z) - q(z) + 4A_-(z)e^{-z^2/2} = 0\\
&A_-(z) = \frac{\gamma(\rho_1) + \gamma(\rho_2)}{2\sqrt{2\pi}}[1 - \rho(z)^2],
\quad A_+(z) = A_-(z)\rho(z)
\end{aligned}
\end{equation}
subject to the boundary conditions $q(z)\to0$ as $z\to\pm\infty$. 
Specifically, when $c_i = c_j$, we have $w_i = w_j = w$ and the total expected effort is reduced to 
\begin{equation}\label{eq-totaleffort-reduced}
M(\tilde{y}_t, t) = \frac{2w\sigma\sqrt{T-t}}{\sqrt{2\pi}}e^{-z^2/2} + o(w)
\end{equation}
\end{theorem}

@@

For more properties of the equilibrium, please refer to \citet{Ryvkin2022Fight}. 
Here, we only provide a supplementary analysis related to contest design:

@@

When generating long-horizon contest data, it is important to appropriately lower the effort costs $c_i$ and $c_j$ to ensure sustained effort from the contestants.
This is because effort levels are influenced by the remaining time until the deadline:
according to equation~(\ref{eq-equilibrium-effort}), the further away the deadline, the lower the equilibrium effort. 
Moreover, with volatility held constant, a long contest duration increases the likelihood that the true output gap undergoes a random walk to an unusually high level, potentially resulting in unexpected early success \citep{Ryvkin2022Fight}.
These factors may affect the quality of the generated data.

@@

%%%%%%%%%% Figure & Table %%%%%%%%%%%
\noindent
\begin{minipage}[t]{0.43\textwidth}
	\vspace*{\fill}
	\centering
	\includegraphics[width=\linewidth]{validate_lamb.pdf}
	\vspace*{\fill}
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
	\vspace*{\fill}
	\centering
	\newcolumntype{Y}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{llYY}
		\toprule
		& coef. & stderr & 95\% CI \\
		\midrule
		const.
		& -0.8.30 & 3.122 & [-7.051, 5.392] \\
		$\log(1 + \hat{\lambda})$ 
		& 3.288\textbf{**} & 1.067 & [1.161, 5.416] \\
		\midrule
		Obs. & \multicolumn{3}{c}{75} \\
		R$^2$ & \multicolumn{3}{c}{0.115} \\
		Adj. R$^2$ & \multicolumn{3}{c}{0.103} \\
		\bottomrule
		\addlinespace[0.5ex]
	\end{tabularx}
	\begin{minipage}{\textwidth}
{\footnotesize
\textit{Note:} (1) Significance levels: \textbf{***} $p < 0.001$, \textbf{**} $p < 0.01$, \textbf{*} $p < 0.05$. 
(2) Normality diagnostics: Omnibus = 0.449, Jarque-Bera = 0.091, Skewness = 0.016, Kurtosis = 3.168. 
(3) Other diagnostic statistics: Condition Number = 28.2, Durbin-Watson = 2.212.
}
	\end{minipage}
	\vspace*{\fill}
\end{minipage}
%%%%%%%%%%%% Captions %%%%%%%%%%%%
\noindent
\begin{minipage}[t]{\textwidth}
	\centering
	\captionof{figure}{$\lambda^{\text{MLE}}$ vs. Bayesian Estimate $\hat\lambda$}
	\label{fig-validate-lambda}
\end{minipage}
%\hfill
%\begin{minipage}[t]{0.53\textwidth}
%	\centering
%	\captionof{table}{Regression of $\lambda^{\text{MLE}}$ on Bayesian Estimate $\hat\lambda$}
%\end{minipage}
\medskip

The left panel of Figure~\ref{fig-validate-lambda} reveals a clear positive relationship between the log-transformed estimates of $\hat\lambda$ and $\lambda^{\text{MLE}}$.
In the accompanying regression table, we observe that the intercept is statistically insignificant, while the slope coefficient is estimated at 3.288 and is statistically significant at the 1\% level. 
The regression residuals exhibit no significant deviation from normality, as indicated by the low Jarque-Bera statistic (0.091), near-zero skewness (0.016), and kurtosis close to 3 (3.168). 
The condition number (28.2) suggests no severe multicollinearity, while the Durbin-Watson statistic (2.212) indicates no significant autocorrelation in the residuals. 
These diagnostics support the validity of the OLS assumptions.

It is worth noting, however, that the $R^2$ of the regression is relatively low, around 0.1, suggesting that the scatter points are not tightly clustered around the fitted line but instead show substantial dispersion.
This pattern likely reflects the limited sample size as well as the simplifying assumptions introduced during data processing and structural estimation.
